Analysis of the 2005--\myrevision{2016} Earthquake Sequence in Northern Iran Using the Visibility Graph Method

### 2017-06-21 results.tex
update (cont.) to paag revision

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06-rev.pdf} 
	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran. The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope. The color version of this figure is available only in the electronic edition.}
	\label{fig:km}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-07-rev.pdf} 
	\caption{Correlation between $k$-$M$ slope and $b$-value as drawn from the results of the present study for the region of northern Iranian and three other previous studies, including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, and results from two experiments \citep{Telesca2014-pone}. The lines represent linear regressions obtained to fit the different data points, considering different combinations. The values of the correlation coefficient, $R$, are indicated for each regression line. The color version of this figure is available only in the electronic edition.}
	\label{fig:regression}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06} 
	\caption{Scattered distribution of events in the magnitude-connectivity degree plane and linear regressions obtained for the $k$-$M$ relationships for the three seismic regions in northern Iran. The value next to each of regression line corresponds to the slope of the line, which is referred here as the $k$-$M$ slope. The color version of this figure is available only in the electronic edition.}
	\label{fig:km}
\end{figure*}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-07} 
	\caption{\myrevision{Correlation between $k$-$M$ slope ($m$) and the $b$ value as drawn from the results of the present study for the region of northern Iranian using the complete (a) and declustered (b) catalogs, along with other previous studies including analysis of the Mexican subduction zone \citep{Telesca2013}, the Pannonian seismic zone \citep{Telesca2014}, southern California \citep{Azizzadeh_2017_SSA}, and results from two experiments \citep{Telesca2014-pone}. The lines represent linear regressions obtained to fit the different data points, considering different combinations. The values of the correlation coefficient, $R$, are indicated for each regression line. The color version of this figure is available only in the electronic edition.}}
	\label{fig:regression}
\end{figure*}
